Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-11-14 inst/examples/20170201-manuscript.Rmd
ok

cities <- c(
	      "Greifswald",
	      "Lund",
	      "Other",
	      "Stockholm",
	      "Tartu",
	      "Turku",
	      "Uppsala",
	      "Vyborg",
	      "Gothenburg",
	      "Linkoping"
	    )
city.colors <- stata_pal("s2color")(length(city.colors))
names(city.colors) <- cities

@@

brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
labs <- brs; labs[!brs %in% df$publication_decade] <- ""
p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(shape = publication_place, color = publication_place), size = 5) +
       xlab("Decade") +
       ylab("Title count per capita (n)") +
       #scale_color_stata() +
       scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) +                      
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = labs) +                    
       #ggtitle("Title count per capita") +
       ggtitle("Figure 12") +       
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) 
print(p)

@@

df <- bind_rows(df1, df2)
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
brsy <- seq(0, round(max(df$n), -3), 1e3)
labs <- brs; labs[!brs %in% df$publication_decade] <- ""
p <- ggplot(df, aes(x = publication_decade, y = n)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
       xlab("Decade") +
       ylab("Title count (n)") +
       #ggtitle("Title count (absolute)") +
       ggtitle("Figure 13") +              
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = labs) +
       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 1)) +
       scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) +       
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) 
       #scale_color_stata()
print(p)
```

@@

df <- bind_rows(df1, df2)
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = paper)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
       xlab("Decade") +
       ylab("Paper (sheets)") +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_y_continuous(label = scientific_10) +
       ggtitle("Figure 14") +
       scale_color_manual(values = city.colors[as.character(levels(df$publication_place))]) +       
       guides(shape = guide_legend(title = "Place"), color = guide_legend(title = "Place")) 
       #scale_color_stata()
print(p)
```

@@

# PAPER CONSUMPTION
theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language, color = language), size = 5) +
       geom_line(aes(color = language), size = 1) +       
       xlab("Decade") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"), color = guide_legend(title = "Language")) +
       #scale_color_stata() +
       scale_color_manual(values = lang.colors[as.character(levels(df$language))]) +         
       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +       
       scale_y_continuous(label = scientific_10) +
       ggtitle("Figure 19")       
       # ggtitle(paste("Devotional literature (", catalogue, ")", sep = ""))

>>>>

cities <- c(
	      "Greifswald",
	      "Lund",
	      "Other",
	      "Stockholm",
	      "Tartu",
	      "Turku",
	      "Uppsala",
	      "Vyborg",
	      "Gothenburg",
	      "Linköping"
	    )
city.colors <- stata_pal("s2color")(length(city.colors))
names(city.colors) <- cities

@@

brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
labs <- brs; labs[!brs %in% df$publication_decade] <- ""
p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(shape = publication_place, color = publication_place), size = 5) +
       xlab("Decade") +
       ylab("Title count per capita (n)") +
       #scale_color_stata() +
       #scale_color_manual(values = city.colors[as.character(levels(dfm$publication_place))]) +
       scale_color_manual(values = city.colors[match(unique(dfm$publication_place), names(city.colors))]) +              
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = labs) +                    
       #ggtitle("Title count per capita") +
       ggtitle("Figure 12") +       
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) 
print(p)

@@

df <- bind_rows(df1, df2)
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
brsy <- seq(0, round(max(df$n), -3), 1e3)
labs <- brs; labs[!brs %in% df$publication_decade] <- ""
#df$publication_place <- factor(df$publication_place, levels = levels(df0$publication_place))

p <- ggplot(df, aes(x = publication_decade, y = n)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
       xlab("Decade") +
       ylab("Title count (n)") +
       ggtitle("Figure 13") +              
       scale_x_continuous(breaks = brs, labels = labs) +
       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 1)) +
       scale_color_manual(values = city.colors[match(unique(df$publication_place), names(city.colors))]) +       
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place"))

@@

df <- bind_rows(df1, df2)
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = paper)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
       xlab("Decade") +
       ylab("Paper (sheets)") +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_y_continuous(label = scientific_10) +
       ggtitle("Figure 14") +
       scale_color_manual(values = city.colors[match(unique(df$publication_place), names(city.colors))]) +       
       guides(shape = guide_legend(title = "Place"), color = guide_legend(title = "Place")) 
       #scale_color_stata()
print(p)
```

@@

# PAPER CONSUMPTION
theme_set(theme_bw(20))
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language, color = language), size = 5) +
       geom_line(aes(color = language), size = 1) +       
       xlab("Decade") +
       ylab("Paper (sheets)") +
       guides(shape = guide_legend(title = "Language"), color = guide_legend(title = "Language")) +
       #scale_color_stata() +
       #scale_color_manual(values = lang.colors[as.character(levels(df$language))]) +
       scale_color_manual(values = lang.colors[match(unique(df$language), names(lang.colors))]) +              
       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2)) +       
       scale_y_continuous(label = scientific_10) +
       ggtitle("Figure 19")       
       # ggtitle(paste("Devotional literature (", catalogue, ")", sep = ""))
